Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-11-07 sports_analytics.Rmd
Added a bunch of papers on gambling.

@Boulier2017

@@

>>>>

@Boulier2006: Testing the efficiency of the National Football League betting market: Look at 1994 - 2000.  Conclude there is no evidence to conclude the market was inefficient over this period of time.

Boulier, B. L. and Stekler, H. O. (2003). Predicting the outcomes of National Football League games. International Journal of Forecasting 19 257{270. : They test several predictors for NFL games and find that the betting market is the best predictor.

Buttrey, S. E. (2016). Beating the market betting on NHL hockey games. Journal of Quantitative
Analysis in Sports 12 87{98. : They demonstrate a method that produced a positive ROI

Gandar, J., Zuber, R., O'brien, T. and Russo, B. (1988). Testing rationality in the point spread
betting market. The Journal of Finance 43 995{1008. : They conclude that Stats test are too weak to reject the hypothesis of rationality.  But they do reject rationalist with ``economic tests".

Lacey, N. J. (1990). An estimation of market efficiency in the NFL point spread betting market. Applied Economics 22 117{129. : Finds the market to be efficient, though they did find some profitable betting rules over the period of time between 1984 and 1986

@@

#Betting pools
Breiter DJ, Carlin BP (1997) How to play office pools if you must.Chance10(1):5–11

Clair B, Letscher D (2007) Optimal strategies for sports betting pools.Oper. Res.55(6):1163–1177.

Kaplan EH, Garstka SJ (2001) March Madness and the office pool.Management Sci.47(3):369–382

Metrick A (1996) March Madness? Strategic behavior in {NCAA}basketball tournament betting pools.J. Econom. Behav. Organ.30(2):159–172.

Niemi JB, Carlin BP, Alexander JM (2008) Contrarian strategies forNCAA tournament pools: A cure for March Madness?Chance21(1):35–42

Sauer RD (1998) The economics of wagering markets.J. Econom. Lit-erature36(4):2021–2064

Computing the Number of Winning NFL Survivor Pool Entries
J Imbrogno, D Bergman - The College Mathematics Journal, 2022:
Description: The average number of winning survivor pool entries is computed for the 2019 National Football League (NFL) season. The probability of having to share the winning pot, given realistic expectations on game outcomes, is also shown.

Nichols, M. W. (2012). The impact of visiting team travel on game outcome and biases in NFL betting markets. Journal of Sports Economics 15 78{96. : They conclude that the impact of travel os not completely incorporated into the betting markets, but that any effect is too small to find anye profitable advantage.

Paul, R. J. and Weinbach, A. P. (2014). Market efficiency and behavioral biases in the wnba betting market. International Journal of Financial Studies 2 193{202.: Over the period of 2007–2012, they find that the market is still hard to beat.

Soebbing, B. P. and Humphreys, B. R. (2013). Do gamblers think that teams tank? Evidence from the NBA. Contemporary Economic Policy 31 301{313.
Spann, M. and Skiera, B. (2009). Sports forecasting: a: NBA bettors believe that tanking is occurring.
